Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2023-12-31 Manuscript_Nater_etal.qmd
Added results for detection parameters

# Printing function
printPostSum <- function(table, row = NULL, area = NULL){

@@

@@

# Detection stats
#Det.hyper.mean
#Det.sd.spatial
#Det.sd.temporal
#Det.sd.residual
#Det.min
#Det.max

@@

Recruitment rates varied between `r R.min$post.sum` (area "`r R.min$area.name`") and `r R.max$post.sum` (area "`r R.max$area.name`") and displayed a spatial pattern opposite to that 
of annual survival, i.e. lower recruitment rates co-occurring with higher survival rates and vice-versa [@fig-pVRB; @fig-paramCorrs B). Across all areas and years, average recruitment rate was `r R.hyper.mean$post.sum`. Unlike for survival, the model predicted similar magnitudes of spatial and temporal variation (random effect SDs of `r R.sd.spatial$post.sum` and `r R.sd.temporal$post.sum`, respectively), and about twice as much residual variation (`r R.sd.residual$post.sum`).

@@

>>>>

# Printing function
printPostSum <- function(table, row = NULL, area = NULL, exp = FALSE, pCalc = FALSE){

@@

  if(exp){
    table$Median <- exp(table$Median)
    table$lCI <- exp(table$lCI)
    table$uCI <- exp(table$uCI)
  }

  if(pCalc){
     pi <- 3.141593
     W <- 200
     table$Median <- sqrt((pi*table$Median^2)/2)/W
     table$lCI <- sqrt((pi*table$lCI^2)/2)/W
     table$uCI <- sqrt((pi*table$uCI^2)/2)/W
  }

@@

# Detection stats
Det.hyper.mean <- printPostSum(table = post.sum$hParams.sum, 
                              row = which(post.sum$hParams.sum$Parameter == "h.mu.dd"),
                              exp = TRUE)
pDet.hyper.mean <- printPostSum(table = post.sum$hParams.sum, 
                              row = which(post.sum$hParams.sum$Parameter == "h.mu.dd"),
                              exp = TRUE, pCalc = TRUE)

Det.sd.spatial <- printPostSum(table = post.sum$hParams.sum,
                             row = which(post.sum$hParams.sum$Parameter == "h.sigma.dd"))
Det.sd.temporal <- printPostSum(table = post.sum$hParams.sum,
                             row = which(post.sum$hParams.sum$Parameter == "sigmaT.dd"))
Det.sd.residual <- printPostSum(table = post.sum$hParams.sum,
                             row = which(post.sum$hParams.sum$Parameter == "sigmaR.dd"))
Det.min <- printPostSum(table = post.sum$detect.sum, 
                      row = which(post.sum$detect.sum$Median == min(post.sum$detect.sum$Median)))

pDet.min <- printPostSum(table = post.sum$detect.sum, 
                      row = which(post.sum$detect.sum$Median == min(post.sum$detect.sum$Median)),
                      pCalc = TRUE)

Det.max <- printPostSum(table = post.sum$detect.sum,
                      row = which(post.sum$detect.sum$Median == max(post.sum$detect.sum$Median)))

pDet.max <- printPostSum(table = post.sum$detect.sum,
                      row = which(post.sum$detect.sum$Median == max(post.sum$detect.sum$Median)),
                      pCalc = TRUE)

@@

Recruitment rates varied between `r R.min$post.sum` (area "`r R.min$area.name`") and `r R.max$post.sum` (area "`r R.max$area.name`") and displayed a spatial pattern opposite to that 
of annual survival, i.e. lower recruitment rates co-occurring with higher survival rates and vice-versa (@fig-pVRB; @fig-paramCorrs B). Across all areas and years, average recruitment rate was `r R.hyper.mean$post.sum`. Unlike for survival, the model predicted similar magnitudes of spatial and temporal variation (random effect SDs of `r R.sd.spatial$post.sum` and `r R.sd.temporal$post.sum`, respectively), and about twice as much residual variation (`r R.sd.residual$post.sum`).

@@

Detection decay parameters, which determine detection probability in distance sampling surveys, varied across areas from between `r Det.min$post.sum` in "`r Det.min$area.name`" to `r Det.max$post.sum` in "`r Det.max$area.name`, resulting in detection probabilities over the transect sites (truncation distance = 200 m) from `r pDet.min$post.sum` to `r pDet.max$post.sum`, respectively. 
The global average detection decay was `r Det.hyper.mean$post.sum` (detection probability = `r pDet.hyper.mean$post.sum`), and in general, higher values were more common in the Southern half of the country than the Northern half (SF "Avg_detect_Map.pdf").
Variation in detection over time was modest (SF "TimeSeries_pDetect.pdf"), and among-year variation in detection decay (random effect log SD = `r Det.sd.temporal$post.sum`) was almost identical in magnitude to spatial (`r Det.sd.spatial$post.sum`) and residual (`r Det.sd.residual$post.sum`) variation.
